Fréchet Distance

### 2022-12-05 docs/paper.tex
fix typos

\begin{mydef}
  \label{def_hausdorff_distance}
  Given two (polygonal) curves $P$ and $Q$, 
  their Hausdorff distance $\delta_{hd}(P,Q)$ is mathematically defined as: 
  $$\delta_{hd}(P,Q) = \max \left( \sup_{p \in P} \inf_{q \in Q} \text{dist}(p,q), \sup_{q \in Q} \inf_{p \in P} \text{dist}(p,q) \right)$$
\end{mydef}

@@

\section{Algorithms}
\label{sec_algorithms}
% Chapter summary and structure
Several algorithms to compute the Fréchet distance of polygonal curves were proposed, 
starting from the Original algorithm for the continuous variant by Alt and Godau in 1995 \cite{alt_computing_1995}.
The algorithm is based on a concept called free-space diagram and gives a baseline for newer improved versions, 
e.g., the version by Buchin et al. \cite{buchin_four_2017}. 
This chapter is structured as follows: 
first the original algorithm for the continuous Fréchet distance is described in \autoref{sec_original_algorithm},
then in \autoref{sec_improved_algorithm} a more recent improved algorithm for the same problem is given.
Afterwards, the modification necessary to compute the weak variant are described in \autoref{sec_weak_algorithm}.
Finally, an algorithm to compute the discrete Fréchet distance is given in \autoref{sec_discrete_algorithm}.
% Finally

@@

We start by looking at the simplest case for two polygonal curves with two vertices each, i.e., two line segments.
The free space is are all valid combinations of positions on $P$ and $Q$ that have a distance of at most $\varepsilon$.
Therefore, we define $F_\varepsilon = \{(s,t) \in [0,1]^2 \ | \ dist(P(s), Q(t)) \leq \varepsilon \}$.
Plotting $s$ and $t$ on a two-dimensional graph, while indicating all illegal combinations in 
another color, gives the free space diagram, see \autoref{fig_free_space}. \cite{alt_computing_1995}

>>>>

\begin{mydef}
  \label{def_hausdorff_distance}
  Given two normal or polygonal curves $P$ and $Q$, 
  their Hausdorff distance $\delta_{hd}(P,Q)$ is mathematically defined as: 
  $$\delta_{hd}(P,Q) = \max \left( \sup_{p \in P} \inf_{q \in Q} \text{dist}(p,q), \sup_{q \in Q} \inf_{p \in P} \text{dist}(p,q) \right)$$
\end{mydef}

@@

\section{Algorithms}
\label{sec_algorithms}
% Chapter summary and structure
Several algorithms to compute the Fréchet distance of polygonal curves were proposed, 
starting from the Original algorithm for the continuous variant by Alt and Godau in 1995 \cite{alt_computing_1995}.
The algorithm is based on a concept called free-space diagram and gives a baseline for newer improved versions, 
e.g., the version by Buchin et al. \cite{buchin_four_2017}. 
This chapter is structured as follows: 
first the original algorithm for the continuous Fréchet distance is described in \autoref{sec_original_algorithm}.
% then in \autoref{sec_improved_algorithm} a more recent improved algorithm for the same problem is given.
Afterwards, the modification necessary to compute the weak variant are described in \autoref{sec_weak_algorithm}.
Finally, an algorithm to compute the discrete Fréchet distance is given in \autoref{sec_discrete_algorithm}.

@@

We start by looking at the simplest case for two polygonal curves with two vertices each, i.e., two line segments.
The free space is all valid combinations of positions on $P$ and $Q$ that have a distance of at most $\varepsilon$.
Therefore, we define $F_\varepsilon = \{(s,t) \in [0,1]^2 \ | \ dist(P(s), Q(t)) \leq \varepsilon \}$.
Plotting $s$ and $t$ on a two-dimensional graph, while indicating all illegal combinations in 
another color, gives the free space diagram, see \autoref{fig_free_space}. \cite{alt_computing_1995}
